A Dependently Typed Multi-Stage Calculus

### 2019-08-29 text/formal-defnition.tex
Comparision with other method.

\AI{Comparison?}

\paragraph{Remark:}
When this function is composed with another piece of code $v$ of type, say,
\(\TW_\gamma \text{Vector }5\), \QPercent plays an essential role; that is,
\(\text{Vector }5\) and \(\text{Vector }(\%_\beta 5)\) are syntactically
different types but \QPercent enables to equate one with another.
Interestingly, Hanada and Igarashi~\cite{Hanada2014} rejected the idea of
reduction that removes $\%_\alpha$ when they developed \LTP{}, as such
reduction does not match the operational behavior of the CSP operator in
implementations. However, as an equational system for multi-stage programs,
the rule \QPercent makes sense.

>>>>

There are other ways to realize the vector addition function for fixed-length
lists: determining statically the length of all the vectors and use tuples
instead of lists or checking dynamically the dimensions of every pair of
lists. However, our method is better than there two methods in two points.
First, our function, $\text{vadd}_1$ can generate function for arbitrary
length vectors unlike ones using tuples. Second, $\text{vadd}_1$ has an
advantage in speed over ones using dynamic checking because it can generate
optimized function for a given length.

\paragraph{Remark:}
When this function is composed with another piece of code $v$ of type, say,
\(\TW_\gamma \text{Vector }5\), \QPercent{} plays an essential role; that is,
\(\text{Vector }5\) and \(\text{Vector }(\%_\beta 5)\) are syntactically
different types but \QPercent{} enables to equate one with another.
Interestingly, Hanada and Igarashi~\cite{Hanada2014} rejected the idea of
reduction that removes $\%_\alpha$ when they developed \LTP{}, as such
reduction does not match the operational behavior of the CSP operator in
implementations. However, as an equational system for multi-stage programs,
the rule \QPercent{} makes sense.
